Accurate spectroscopic estimates of luminosity and distance\\ for luminous red-giant stars

### 2018-07-11 paper/sp.tex
equations

\documentclass[modern]{aastex62}

@@

% math macros
\newcommand{\logg}{\log g}

@@

foo

bar

@@

foo

bar

@@

>>>>

\documentclass[modern]{aastex62}
\usepackage{amsmath}

@@

% math macros
\newcommand{\logg}{\log g}
\DeclareMathOperator*{\argmin}{argmin}

@@

The promise of mapping the Milky Way disk with infrared spectroscopy
and red-giant stars.

The information \gaia\ brings to this.

The history and value (and disadvantages)
of data-driven models for these kinds of problems.

The dangers of aggressive machine-learning methods. Why will we just
look at linear models? The disadvantages of this approach.

The dangers of cutting on \gaia\ properties. Why we will not cut on
\gaia\ parallaxes. The disadvantages of this approach.

@@

The \gaia\ Catalog describes a likelihood function!

There is a parallax offset.

We are only looking at \apogee\ luminous giants (selected spectroscopically).

We use photometry from \gaia, \zmass, \wise.

@@

\begin{eqnarray}
Q_n &\equiv& 0.01\,\varpi_n\,10^{0.2\,K_n}
\\
\sigma_n &\equiv& \sigma_{\varpi n}\,10^{0.2\,K_n}
\\
Q_n &=& \theta_Q\cdot x_n + \mbox{noise}
\\
\chi^2 &\equiv& \sum_{n=1}^N \frac{[Q_n - \theta_Q\cdot x_n]^2}{\sigma_n^2}
\\
\hat{\theta}_Q &\leftarrow& \argmin_{\theta_Q}\left[\frac{1}{2}\,\chi^2 + \lambda_Q\,||\theta_Q||_1^1\right]
\quad ,
\end{eqnarray}
where...

\begin{eqnarray}
Q_n &=& \exp(\theta_M\cdot x_n) + \mbox{noise}
\\
M_{Kn} &\approx& \frac{1}{0.2\,\ln 10}\,\theta_M\cdot x_n
\\
\chi^2 &\equiv& \sum_{n=1}^N \frac{[Q_n - \exp(\theta_M\cdot x_n)]^2}{\sigma_n^2}
\\
\hat{\theta}_M &\leftarrow& \argmin_{\theta_M}\left[\frac{1}{2}\,\chi^2 + \lambda_M\,||\theta_M||_1^1\right]
\quad ,
\end{eqnarray}
where...
